Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-07-09 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added to sec. IV.C and figure captions

\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-??}

@@

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
%  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \caption{
    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    $(\wilson{P}Ê\pm \wilson{P'})$ are identical to $(\wilson{S}Ê\pm \wilson{S'})$,
    apart from a small shift of the contours by $(+0.2,\, +0.15)$.
  }
  \label{fig:scalar}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    Constraints (2D-marginalized) on complex-valued scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in 
    \reftab{tab:observables} (red) at 68\% (darker) and 95\% 
    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
    and $F_H^\mu$ \todo{What else?}
    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vector couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c}) 
  \right]
\end{align}
is numerically of the order ${\cal O}(10^{-7})$ in the SM
\todo{check large SM uncertainty of 30\% at low-$q^2$}
\begin{equation}
\begin{aligned}
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
\\
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. On the other hand, $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensor
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensor and scalar couplings.

@@

We find that the experimental measurement of $F_H^\mu$
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|{\cal C}_{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|{\cal C}_{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of non-standard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar and pseudo-scalar
  couplings due to it's complementarity to $\overline{\cal B}(B_s \to \bar\mu\mu)$.
  Even when taking into account destructive interference with vector couplings
  $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| <
  0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) probability. Currently, the bounds
  from $F_H^\mu$ are not as strong as those from $\overline{\cal B}(B_s \to \bar\mu\mu)$
  by about a factor four. In the future, measurements at LHCb and Belle II will
  further tighten the bounds.

  Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
\item SM-EFT $\ldots$
\end{enumerate}

In all cases these \eos{constraints are weakened only slightly} in the presence
of new physics in vector couplings from destructive interference.

In the future this might change once measurements start to probe the SM expectation,
as in this case constraints on the tensor and scalar couplings become so
stringent that the formal suppression of vector couplings by $m_\ell / \sqrt{q^2}$
is overcome. Our study of angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ shows that

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.
  C.B. received partial support from the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgments}

>>>>

\preprint{EOS-2015-??, FLAVOUR(267104)-ERC-107}

@@

\begin{figure*}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_0,2}
%  \includegraphics[width=.32\textwidth]{plots/pdf/scSP_Bsmumu,scSP_FH,sc910SP_K_KstarBR_Bsmumu_4,6}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_FH,sc910SP_K_KstarBR_Bsmumu_0,4}
  \includegraphics[width=.325\textwidth]{plots/pdf/scSP_Bsmumu,sc910SP_K_KstarBR_Bsmumu_2,6}
  \caption{
    The constraints on complex-valued $\wilson{S,\,S',\,P,\,P'}$
    from $i)$ only $F_H^\mu$~(grey dotted), $ii)$ only $\overline{\cal B}(B_s \to \bar\mu\mu)$
    (blue dashed) and $iii)$ their combination with other data in \reftab{tab:observables}
    as well as non-zero $\wilson[]{9,\,9',\,10,\, 10'}$ (red solid)
    at 68\% (darker) and 95\% (lighter) probability. The constraints on
    Re$(\wilson{P}Ê\pm \wilson{P'})$ are identical to Re$(\wilson{S}Ê\pm \wilson{S'})$,
    apart from a small shift of the contours by $(+0.2,\, +0.15)$. The SM is indicated
    by the black diamond.
  }
  \label{fig:scalar}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_0,2}
  \includegraphics[width=.35\textwidth]{plots/pdf/smEFTS_K_Bsmumu,smEFTS10_K_KstarBR_Bsmumu_1,3}
  \caption{
    Constraints (2D-marginalized) on complex-valued scalar couplings 
    $\wilson{S,\,S'}$ in the scenario SM-EFT from all data in 
    \reftab{tab:observables} (red) at 68\% (darker) and 95\% 
    (lighter) probability when marginalising over non-zero $\mbox{Re, Im}
    (\wilson[NP]{10,\,10'}) \in [-7,\,7]$.
    For comparison the according constraints from only $\overline{\cal B}(B_s\to \bar\mu\mu)$
    and $F_H^\mu$ \todo{What else?}
    (dashed blue contours) at 68\% (inner) and 95\% (outer) probability.
    The SM is indicated by the black diamond.
  }
  \label{fig:scalar:SM-EFT}
\end{figure*}

@@

For comparison, the SM estimates are also given in \reftab{tab:postdictions}
multiplied by the $B^0$-meson life time $\tau_{B^0} = 1.519$~ps.
At low-$q^2$ they are of order ${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and
$(J_{1c} + J_{2c})$, getting suppressed down to ${\cal O}(10^{-10})$ at high-$q^2$
due to the $m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical
magnitude of vector couplings, note that for example the branching ratio of
$B\to K^*\bar\ell\ell$
\begin{align}
  \frac{{\rm d}\BR}{{\rm d}q^2} & = \frac{\tau_{B^0}}{3} \left[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c}) 
  \right]
\end{align}
is numerically of the order ${\cal O}(10^{-7})$ in the SM
\begin{equation}
\begin{aligned}
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[1.1,\, 6]} & =
  \left(1.86_{-0.44}^{+0.53} \right) \cdot 10^{-7} \,,
\\
  \langle {\rm d}\BR/{\rm d}q^2 \rangle_{[15,\, 19]} & =
  \left(1.91_{-0.16}^{+0.16} \right) \cdot 10^{-7} \,,
\end{aligned}
\end{equation}
when integrated over low- and high-$q^2$ regions. \todo{Elaborate on larger
theory uncertainties at low-$q^2$, due to subleading corrections.
Form factor uncertainties are small due to correlations, would be larger
when neglecting them.}

The angular observable $J_{6c}$
is strictly zero for the approximation adopted here. Non-zero contributions
can be generated by QED corrections or potentially from higher-dimensional
($d \geq 8$) $|\Delta B| = |\Delta S| = 1$ operators, leading to parametrical
suppression of $\alpha_e/(4 \pi)$ or $(m_b/m_W)^2$, respectively. Such a
suppression must be compared to potential suppression present for tensor
and scalar contributions in particular NP models in order to decide their
relevance. Our model-independent fits are still in a realm where such
considerations are insignificant since current experimental measurements, in
combination with theory uncertainties, do not impose yet too stringent
constraints on tensor and scalar couplings.

@@

We find that the experimental measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
\item imposes by itself constraints on tensor couplings $|\wilson{T,\,T5}|
  < 0.43\, (0.57)$ at 68\% (95\%) probability, superseding previous bounds.
  In combination with current data from $B\to K^* \bar\mu\mu$ and lattice
  $B\to K^*$ form factors they become tighter $|\wilson{T,\,T5}| < 0.33\,
  (0.43)$, even in the presence of non-standard contributions in vector
  couplings.
\item allows for the first time to bound all four scalar couplings $\wilson{i}$ 
  with $i = S,\,S',\,P,\,P'$ due to it's complementarity to $\overline{\cal B}(B_s 
  \to \bar\mu\mu)$. Even when taking into account destructive interference with
  vector couplings, $|\wilson{i} + \wilson{i'}| < 0.3\, (0.6)$ and 
  $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ at 68\% (95\%) 
  probability. Currently, the bounds from $F_H^\mu$ are not as strong as those
  from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a factor four. In the
  future, measurements at LHCb and Belle II will further tighten the bounds.

  Moreover, measurements of $F_H^e$ ($\ell = e$)
  will provide constraints on scalar couplings in the electron channel in
  the lack of measurements of the branching ratio of $B_s \to \bar{e}e$.
\end{enumerate}
Our updated bounds on complex-valued tensor and scalar couplings are summarised
in \reftab{tab:cTT5:1-dimCLs} and \reftab{tab:cSP:1-dimCLs}, accounting also for
interference effects with vector couplings. These bounds hold even in the most 
general scenario of complex-valued tensor, scalar and vector couplings, showing
also that the data is able to bound the real and imaginary parts of all Wilson
coefficients simultaneously.

As a special case, we considered also the scenario arising from the SM augmented
by dimension 6 operators generalising existing studies to the case of complex-valued
couplings. In this scenario tensor couplings are absent and additional
relations between scalar couplings are enforced by the linear realisation of the
$SU(2)_L \otimes U(1)_Y$ electroweak symmetry group.

Our study of yet not measured angular observables $J_{6c}$, $(J_{1c} + J_{2c})$
and $(J_{1s} - 3 J_{2s})$ in $B\to K^* (\to K\pi) \bar\mu\mu$ (see 
\reftab{tab:postdictions}) shows that despite the current bounds on tensor couplings,
enhancements of two orders of magnitude over the SM predictions are allowed for
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. On the other hand, current bounds
on scalar couplings from $B_s\to \bar\mu\mu$ and $F_H^\mu$ are already quite 
restrictive allowing only for small deviations from SM predictions in 
$(J_{1c} + J_{2c})$ and $(J_{1s} - 3 J_{2s})$. Notably, the CP asymmetry 
$A_{\Delta\Gamma}(B_s\to \bar\mu\mu)$ induced by non-vanishing width of the 
$B_s$ meson can still take any value in the range $[-1,\, 1]$.

%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+
\begin{acknowledgments}
  We are grateful to Danny van Dyk for helpful discussions and his support on
  EOS \cite{EOS}. Concerning form factor results from lattice, we thank Chris
  Bouchard and Matthew Wingate for communications on their results of $B\to K$
  \cite{Bouchard:2013eph} and $B\to K^*$ \cite{Horgan:2015vla} form factors,
  respectively. We thank also David Straub for his support with LCSR results of
  $B\to K^*$ form factors \cite{Straub:2015ica}.
  C.B. was supported by the ERC Advanced Grant project ``FLAVOUR''
  (267104).
\end{acknowledgments}
